---
title: "Lab 01 - Hello R"
author: "Annie Somerville"
date: "02/01/2021"
output: github_document
---

## install.packages("usethis")

library(usethis)
use_git_config(user.name = "anniehsom", user.email = "someah19@wfu.edu")

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

 ?datasaurus_dozen

## Exercises

### Exercise 1

The dataset has 1846 rows and 3 columns/variables. The variables are 1) which dataset the data are from, 2) x-values, and 3) y-values.

### Exercise 2

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
  
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

The star data correlation is -.0630, which is slightly less negative than the dino data correlation which is -.0645.

### Exercise 4

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
  
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

The circle data correlation is -.0683, which is slightly more negative than the dino data correlation which is -.0645.


### Exercise 5

```{r plot-all}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

```{r corr-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```
